\cvsection{Work Experience}
\begin{cventries}

    \cventry
    {Manager}
    {State of Minas Gerais Office of the Comptroller General}
    {Belo Horizonte, Brazil}
    {Apr. 2019 - Current}
    {
      \begin{cvitems}
        \item {Management of the fiscal transparency portal of the executive branch of Minas Gerais's state government.}
        \item {Management of the open data portal of the executive branch of Minas Gerais's state government.}
      \end{cvitems}
    }

    \cventry
    {Advisor}
    {State Secretariat Of Planning and Management of Minas Gerais}
    {Belo Horizonte, Brazil}
    {Sep. 2017 - Apr. 2019}
    {
      \begin{cvitems}
        \item {Development of projects aiming to improve the platforms and processes used for budgetary data analysis.}
        \item {Implementation of knowledge management and training initiatives regarding computational tools for data analysis.}
      \end{cvitems}
    }

  \cventry
    {Analyst}
    {State Secretariat Of Planning and Management of Minas Gerais}
    {Belo Horizonte, Brazil}
    {Jan. 2011 - Sep. 2016}
    {
      \begin{cvitems}
        \item {Draft the Fiscal Targets Annex, legal document that establishes the State Medium-Term Fiscal Framework}
        \item {Elaboration of the consolidated statements of the public budget}
        \item {Forecast of revenues and expenditures.}
        \item {Monitoring of fiscal indicators.}
        \item {Scenario analysis for the trajectory of fiscal variables.}
      \end{cvitems}
    }
\end{cventries}
