\cvsection{Work Experience}
\begin{cventries}
  \cventry
    {Specialist in Public Policy and Government Management}
    {State Secretariat Of Planning and Management of Minas Gerais}
    {Belo Horizonte, Brazil}
    {Jan. 2011 - Current}
    {
      \begin{cvitems}
        \item {Draft the Fiscal Targets Annex, legal document that establishes the State Medium-Term Fiscal Framework}
        \item {Elaboration of the consolidated statements of the public budget}
        \item {Forecast of revenues and expenditures.}
        \item {Monitoring of fiscal indicators.}
        \item {Scenario analysis for the trajectory of fiscal variables.}
      \end{cvitems}
    }
  \cventry
    {Intern}
    {State Secretariat Of Planning and Management of Minas Gerais}
    {Belo Horizonte, Brazil}
    {Mar. 2010 - Dec. 2010}
    {
      \begin{cvitems}
        \item {Maintenance of the corporate information system used during the budget elaboration.}
        \item {Actualization of the manual that contained the guidelines for the budget process in the State of Minas Gerais.}
        \item {Generation of the monitoring and evaluation reports of the multiyear plan.}
      \end{cvitems}
    }
    \cventry
    {Intern}
    {Joao Pinheiro Foundation}
    {Belo Horizonte, Brazil}
    {Dec. 2008 - Oct. 2009}
    {
      \begin{cvitems}
        \item {Calculation of indexes used to the distributions of tax revenues (ICMS) collected by the state government but transferred to municipal governments.}
        \item {Participation in the elaboration of the Municipal Finance dimension of the State Index of Social Responsibility.}
      \end{cvitems}
    }  
\end{cventries}
